### 2020-07-03 thesis_template/3_Body/chapter/concept.tex
resolved

\begin{figure}[htb]
    \begin{minipage}[t]{0.2\linewidth}\centering
        \begin{lstlisting}
            struct CustomerOwned {
                key: i32,
                age: i32,
                num_purchase: i32,
                total_purchase: f64,
                duration_spent: f64, 
                duration_since: f64,
                zip_code: String,
                address: String,
                country: String,
                state: String,
                first_name: String,
                last_name: String,
                province: String,
                comment: String, 
                order: OrderOwned
            }
        \end{lstlisting}
      \medskip
      \centerline{(a)}
    \end{minipage}\hfill
    \begin{minipage}[t]{0.6\linewidth}\centering
        \begin{lstlisting}
            struct CustomerBorrowed<'a> {
                key: &'a i32,
                age: &'a i32,
                num_purchase: &'a i32,
                total_purchase: &'a f64,
                duration_spent: &'a f64, 
                duration_since: &'a f64,
                zip_code: &'a String,
                address: &'a String,
                country: &'a String,
                state: &'a String,
                first_name: &'a String,
                last_name: &'a String,
                province: &'a String,
                comment: &'a String, 
                order: &'a OrderBorrowed<'a>
            }
        \end{lstlisting}
      \medskip
      \centerline{(b)}
    \end{minipage}
    \begin{minipage}[t]{0.2\linewidth}\centering
        \begin{lstlisting}
            struct CustomerSlice<'a> {
                key: &'a i32,
                age: &'a i32,
                num_purchase: &'a i32,
                total_purchase: &'a f64,
                duration_spent: &'a f64, 
                duration_since: &'a f64,
                zip_code: &'a str,
                address: &'a str,
                country: &'a str, 
                state: &'a str,
                first_name: &'a str,
                last_name: &'a str,
                province: &'a str,
                comment: &'a str,
                order: &'a OrderSlice<'a>
            }
        \end{lstlisting}
      \medskip
      \centerline{(c)}
    \end{minipage}\hfill
    \begin{minipage}[t]{0.6\linewidth}\centering
        \begin{lstlisting}
            struct CustomerRc {
                key: Rc<i32>,
                age: Rc<i32>,
                num_purchase: Rc<i32>,
                total_purchase: Rc<f64>,
                duration_spent: Rc<f64>,
                duration_since: Rc<f64>,
                zip_code: Rc<String>,
                address: Rc<String>,
                country: Rc<String>,
                state: Rc<String>,
                first_name: Rc<String>,
                last_name: Rc<String>,
                province: Rc<String>,
                comment: Rc<String>,
                order: Rc<OrderRc>
            }
        \end{lstlisting}
      \medskip
      \centerline{(c)}
    \end{minipage}\hfill
    \caption{Representation of Customer objects Whose fields are different variable type: (a) CustomerOwned struct whose fields are all owned 
    (b) CustomerBorrowed struct whose fields are borrowed with reference (c) CustomerSlice struct whose fields are borrowed with slice for sequence value, otherwise reference}
    \label{fig:customer}
 \end{figure}

 \begin{figure}[htb]
    \begin{minipage}[t]{0.2\linewidth}\centering
        \begin{lstlisting}
            struct OrderOwned {
                order_id: i32,
                num_items: i32, 
                payment: f64,
                order_time: f64,
                title: String,
                comment: String
            } 
        \end{lstlisting}
      \medskip
      \centerline{(a)}
    \end{minipage}\hfill
    \begin{minipage}[t]{0.6\linewidth}\centering
        \begin{lstlisting}
            struct OrderBorrowed<'a> {
                order_id: &'a i32,
                num_items: &'a i32, 
                payment: &'a f64,
                order_time: &'a f64,
                title: &'a String,
                comment: &'a String
            }
        \end{lstlisting}
      \medskip
      \centerline{(b)}
    \end{minipage}
    \begin{minipage}[t]{0.2\linewidth}\centering
        \begin{lstlisting}
            struct OrderSlice<'a> {
                order_id: &'a i32,
                num_items: &'a i32, 
                payment: &'a f64,
                order_time: &'a f64,
                title: &'a str,
                comment: &'a str
            }
        \end{lstlisting}
      \medskip
      \centerline{(c)}
    \end{minipage}\hfill
    \begin{minipage}[t]{0.6\linewidth}\centering
        \begin{lstlisting}
            struct OrderRc {
                order_id: Rc<i32>,
                num_items: Rc<i32>,
                payment: Rc<f64>,
                order_time: Rc<f64>,
                title: Rc<String>,
                comment: Rc<String>
            }
        \end{lstlisting}
      \medskip
      \centerline{(c)}
    \end{minipage}\hfill
    \caption{Representation of Order objects Whose fields are different variable type: (a) OrderOwned struct whose fields are all owned 
    (b) OrderBorrowed struct whose fields are borrowed with reference (c) OrderSlice struct whose fields are borrowed with slice for sequence value, otherwise reference}
    \label{fig:order}
 \end{figure}

>>>>

\begin{figure}[htb]
    \begin{minipage}[t]{0.2\linewidth}\centering
        \begin{lstlisting}
            struct CustomerOwned {
                key: i32,
                age: i32,
                num_purchase: i32,
                total_purchase: f64,
                duration_spent: f64, 
                duration_since: f64,
                zip_code: String,
                address: String,
                country: String,
                state: String,
                first_name: String,
                last_name: String,
                province: String,
                comment: String, 
                order: OrderOwned
            }
        \end{lstlisting}
      \medskip
      \centerline{(a)}
    \end{minipage}\hfill
    \begin{minipage}[t]{0.6\linewidth}\centering
        \begin{lstlisting}
            struct CustomerBorrowed<'a> {
                key: &'a i32,
                age: &'a i32,
                num_purchase: &'a i32,
                total_purchase: &'a f64,
                duration_spent: &'a f64, 
                duration_since: &'a f64,
                zip_code: &'a String,
                address: &'a String,
                country: &'a String,
                state: &'a String,
                first_name: &'a String,
                last_name: &'a String,
                province: &'a String,
                comment: &'a String, 
                order: &'a OrderBorrowed<'a>
            }
        \end{lstlisting}
      \medskip
      \centerline{(b)}
    \end{minipage}
    \begin{minipage}[t]{0.2\linewidth}\centering
        \begin{lstlisting}
            struct CustomerSlice<'a> {
                key: &'a i32,
                age: &'a i32,
                num_purchase: &'a i32,
                total_purchase: &'a f64,
                duration_spent: &'a f64, 
                duration_since: &'a f64,
                zip_code: &'a str,
                address: &'a str,
                country: &'a str, 
                state: &'a str,
                first_name: &'a str,
                last_name: &'a str,
                province: &'a str,
                comment: &'a str,
                order: &'a OrderSlice<'a>
            }
        \end{lstlisting}
      \medskip
      \centerline{(c)}
    \end{minipage}\hfill
    \begin{minipage}[t]{0.6\linewidth}\centering
        \begin{lstlisting}
            struct CustomerRc {
                key: Rc<i32>,
                age: Rc<i32>,
                num_purchase: Rc<i32>,
                total_purchase: Rc<f64>,
                duration_spent: Rc<f64>,
                duration_since: Rc<f64>,
                zip_code: Rc<String>,
                address: Rc<String>,
                country: Rc<String>,
                state: Rc<String>,
                first_name: Rc<String>,
                last_name: Rc<String>,
                province: Rc<String>,
                comment: Rc<String>,
                order: Rc<OrderRc>
            }
        \end{lstlisting}
      \medskip
      \centerline{(d)}
    \end{minipage}\hfill
    \caption{Representation of Customer objects Whose fields are different variable type: (a) CustomerOwned struct whose fields are all owned 
    (b) CustomerBorrowed struct whose fields are borrowed with reference (c) CustomerSlice struct whose fields are borrowed with slice for sequence value, otherwise reference 
    (d) CustomerRc struct whose fields are reference counting}
    \label{fig:customer}
 \end{figure}

 \begin{figure}[htb]
    \begin{minipage}[t]{0.2\linewidth}\centering
        \begin{lstlisting}
            struct OrderOwned {
                order_id: i32,
                num_items: i32, 
                payment: f64,
                order_time: f64,
                title: String,
                comment: String
            } 
        \end{lstlisting}
      \medskip
      \centerline{(a)}
    \end{minipage}\hfill
    \begin{minipage}[t]{0.6\linewidth}\centering
        \begin{lstlisting}
            struct OrderBorrowed<'a> {
                order_id: &'a i32,
                num_items: &'a i32, 
                payment: &'a f64,
                order_time: &'a f64,
                title: &'a String,
                comment: &'a String
            }
        \end{lstlisting}
      \medskip
      \centerline{(b)}
    \end{minipage}
    \begin{minipage}[t]{0.2\linewidth}\centering
        \begin{lstlisting}
            struct OrderSlice<'a> {
                order_id: &'a i32,
                num_items: &'a i32, 
                payment: &'a f64,
                order_time: &'a f64,
                title: &'a str,
                comment: &'a str
            }
        \end{lstlisting}
      \medskip
      \centerline{(c)}
    \end{minipage}\hfill
    \begin{minipage}[t]{0.6\linewidth}\centering
        \begin{lstlisting}
            struct OrderRc {
                order_id: Rc<i32>,
                num_items: Rc<i32>,
                payment: Rc<f64>,
                order_time: Rc<f64>,
                title: Rc<String>,
                comment: Rc<String>
            }
        \end{lstlisting}
      \medskip
      \centerline{(d)}
    \end{minipage}\hfill
    \caption{Representation of Order objects Whose fields are different variable type: (a) OrderOwned struct whose fields are all owned 
    (b) OrderBorrowed struct whose fields are borrowed with reference (c) OrderSlice struct whose fields are borrowed with slice for sequence value, otherwise reference 
    (d) OrderRc struct whose fields are reference counting}
    \label{fig:order}
 \end{figure}
